### 2014-12-12 text/Chapter05.tex
Proofreading and English conventions (Chapter 4)

\chapter{Structural coeffect calculus} 
\label{ch:structural}

@@

\noindent
In the flat coeffect calculus, we used the $\czip$ operation to merge the annotations of contexts
available from the declaration-site and the call-site or, in the syntactic reading, to split the 
context requirements.

>>>>

\chapter{The structural coeffect calculus} 
\label{ch:structural}

@@

\noindent
In the flat coeffect calculus, we used the $\czip$ operation to merge the annotations of contexts
available from the declaration site and the call site or, in the syntactic reading, to split the 
context requirements.

### 2014-12-12 text/Chapter06.tex
Finish proofreading and tweaking (Chapter 3)
Proofreading and English conventions (Chapter 4)

\chapter{Unified coeffect language} 
\label{ch:unified}

@@

\begin{compactitem}
\item[-] $[\mathbb{C}, \mathbb{D}]$ is a category of functors between categories $\mathbb{C}$ and $\mathbb{D}$
\item[-] $B^A$ is an exponential object $A \Rightarrow B$ in cartesian closed category
\end{compactitem}

@@

Using lattice-based coeffect structure leads to the typing rules shown in Figure~\ref{fig:unified-lattice-types}.
In the flat coeffect system, this affects both application and abstraction -- in abstraction,
the context-requirements of the body should be smaller than the context available on the 
call-site and declaration-site. In application, we require more than what is required by
the sub-expressions.

>>>>

\chapter{Unified coeffect language ???} 
\label{ch:unified}

@@

\begin{compactitem}
\item[-] $[\mathbb{C}, \mathbb{D}]$ is a category of functors between categories $\mathbb{C}$ and $\mathbb{D}$
\item[-] $B^A$ is an exponential object $A \Rightarrow B$ in a Cartesian-closed category
\end{compactitem}

@@

Using lattice-based coeffect structure leads to the typing rules shown in Figure~\ref{fig:unified-lattice-types}.
In the flat coeffect system, this affects both application and abstraction -- in abstraction,
the context-requirements of the body should be smaller than the context available on the 
call site and declaration site. In application, we require more than what is required by
the sub-expressions.

### 2014-12-12 text/backup/Chapter01.tex
Proofreading and English conventions (Chapter 4)

Effect systems introduced track actions such as memory operations or communication. They are described 
by typing judgments of a form $\Gamma \vdash e : \alpha, \sigma$ where $\Gamma$ is the context of a 
program (typically available variables), $e$ is the expression (program) itself, $\alpha$ is the type of 
values returned by the program (e.g. integer or boolean) and $\sigma$ is a set of possible effects. The 
judgment states that, given the context $\Gamma$, an expression has a type $\alpha$ and can only perform 
effects specified by the set $\sigma$. Wadler and Thiemann \cite{monads-effects-marriage} explain how 
this shapes effect analysis of a lambda abstraction -- that is, how effect systems analyze the effects 
associated with a definition of a function:
%
\begin{quote} 
\emph{In the rule for abstraction, the effect is empty because evaluation immediately
returns the function, with no side effects. The effect on the function arrow
is the same as the effect for the function body, because applying the function will
have the same side effects as evaluating the body.}
\end{quote}
%
This means that, when a programmer defines a function, the system records that executing the 
function will perform the effects of the body of the function. However, simply defining a function
is an effect-free computation. Tate \cite{effects-producer-semantics} calls such effect systems
\emph{producer} effect systems and generalizes the idea of function to more general ``thunking'':
%
\begin{quote}
\emph{We will define an effect as a producer effect if all computations with that effect 
can be thunked as "pure" computations for a domain-specific notion of purity.}
\end{quote}
%
In contrast to the static analysis of (producer) effect systems, the analysis of 
\emph{context-dependence} does not match this pattern. In the systems we consider, lambda 
abstraction places requirements on both the \emph{call-site} (latent requirements) and the 
\emph{declaration-site} (immediate requirements), resulting in different syntactic properties. 
We informally discuss three examples first that demonstrate how contextual requirements propagate.

@@

This example demonstrates how lambda abstraction behaves for context-dependent computations. The 
context requirement of the function body is a set of resources $\{\ident{Clock}, \ident{News}\}$.
The context requirements are split between the \emph{declaration-site} and \emph{call-site}.
However, there are multiple possible splittings. The splitting $\{\ident{News}\} \cup \{\ident{Clock}\}$
models the case when the database is accessed from the server, but time is taken from the client,
while the splitting $\{\ident{Clock}, \ident{News}\} \cup \{\}$ corresponds to the case when both
resources are accessed from the server.

@@

For example, if we wrapped the earlier example above in a function taking \ident{a} (and using 
\ident{b} from the declaration-site) then the function would have context requirements $5$ -- that
is the number associated with the variable \ident{a}.

>>>>

Effect systems introduced track actions such as memory operations or communication. They are described 
by typing judgments of a form $\Gamma \vdash e : \alpha, \sigma$ where $\Gamma$ is the context of a 
program (typically available variables), $e$ is the expression (program) itself, $\alpha$ is the type of 
values returned by the program (e.g. integer or boolean) and $\sigma$ is a set of possible effects. The 
judgment states that, given the context $\Gamma$, an expression has a type $\alpha$ and can only perform 
effects specified by the set $\sigma$. Wadler and Thiemann \cite{monads-effects-marriage} explain how 
this shapes effect analysis of a lambda abstraction -- that is, how effect systems analyze the effects 
associated with a definition of a function:
%
\begin{quote} 
\emph{In the rule for abstraction, the effect is empty because evaluation immediately
returns the function, with no side effects. The effect on the function arrow
is the same as the effect for the function body, because applying the function will
have the same side effects as evaluating the body.}
\end{quote}
%
This means that, when a programmer defines a function, the system records that executing the 
function will perform the effects of the body of the function. However, simply defining a function
is an effect-free computation. Tate \cite{effects-producer-semantics} calls such effect systems
\emph{producer} effect systems and generalizes the idea of function to more general ``thunking'':
%
\begin{quote}
\emph{We will define an effect as a producer effect if all computations with that effect 
can be thunked as "pure" computations for a domain-specific notion of purity.}
\end{quote}
%
In contrast to the static analysis of (producer) effect systems, the analysis of 
\emph{context-dependence} does not match this pattern. In the systems we consider, lambda 
abstraction places requirements on both the \emph{call site} (latent requirements) and the 
\emph{declaration site} (immediate requirements), resulting in different syntactic properties. 
We informally discuss three examples first that demonstrate how contextual requirements propagate.

@@

This example demonstrates how lambda abstraction behaves for context-dependent computations. The 
context requirement of the function body is a set of resources $\{\ident{Clock}, \ident{News}\}$.
The context requirements are split between the \emph{declaration site} and \emph{call site}.
However, there are multiple possible splittings. The splitting $\{\ident{News}\} \cup \{\ident{Clock}\}$
models the case when the database is accessed from the server, but time is taken from the client,
while the splitting $\{\ident{Clock}, \ident{News}\} \cup \{\}$ corresponds to the case when both
resources are accessed from the server.

@@

For example, if we wrapped the earlier example above in a function taking \ident{a} (and using 
\ident{b} from the declaration site) then the function would have context requirements $5$ -- that
is the number associated with the variable \ident{a}.
